\documentclass[a4paper,14pt]{extarticle}

\input{preamble.tex}

\begin{document}
\input{title.tex}% это титульный лист
\newpage
\setcounter{page}{2}

{
    \hypersetup{linkcolor=black}
    \tableofcontents
}

% \newpage
% \input{sections/examples.tex}

\newpage
\input{sections/1-formulation-of-problem.tex}

\newpage
\input{sections/2-relevance.tex}

\newpage
\input{sections/3-existing-projects.tex}

\newpage
\input{sections/4-tech-stack.tex}

\newpage
\input{sections/5-architecture.tex}

% \clearpage
% \input{sections/6-system-description.tex}

\clearpage
\input{sections/7-testing.tex}

\newpage
\input{sections/8-future.tex}

\newpage
\input{sections/9-usage.tex}

\newpage
\input{sections/10-code-base.tex}

\newpage
\input{sections/11-my-contribution.tex}



\newpage

\begin{thebibliography}{0}
    \bibitem{spring Baeldung}\hypertarget{spring baeldung}{}
    \href{https://www.baeldung.com/spring-boot}
    {Ligios A\@. Introduction to Spring Boot. --- Baeldung, 2023.}

    \bibitem{grpc official}\hypertarget{grpc official}{}
    \href{https://grpc.io/docs/}
    {Official gRPC Documentation. --- gRPC, 2024.}

    \bibitem{scylladb}\hypertarget{scylladb}{}
    \href{https://www.scylladb.com/}
    {ScyllaDB Documentation. --- ScyllaDB, 2024.}

    \bibitem{openapi}\hypertarget{openapi}{}
    \href{https://www.openapis.org/}
    {OpenAPI Specification. --- OpenAPI Initiative, 2023.}

    \bibitem{helm}\hypertarget{helm}{}
    \href{https://helm.sh/docs/}
    {Official Helm Documentation. --- Helm, 2024.}

    \bibitem{kubernetes}\hypertarget{kubernetes}{}
    \href{https://kubernetes.io/docs/}
    {Kubernetes Documentation. --- Kubernetes, 2024.}

    \bibitem{grafana}\hypertarget{grafana}{}
    \href{https://grafana.com/docs/}
    {Grafana Documentation. --- Grafana Labs, 2024.}

    \bibitem{loki}\hypertarget{loki}{}
    \href{https://grafana.com/docs/loki/latest/}
    {Loki Documentation. --- Grafana Labs, 2024.}

    \bibitem{minikube}\hypertarget{minikube}{}
    \href{https://minikube.sigs.k8s.io/docs/}
    {Minikube Documentation. --- Minikube, 2024.}

    \bibitem{jpa Baeldung}\hypertarget{jpa baeldung}{}
    \href{https://www.baeldung.com/jpa-entities}
    {balasubramaniam v\@. defining jpa entities| baeldung. --- 2021.}

    \bibitem{docker Baeldung}\hypertarget{docker baeldung}{}
    \href{https://www.baeldung.com/ops/docker-compose}
    {Ligios A\@. Introduction to Docker Compose. --- Baeldung, 2023.}

    \bibitem{java shild} \hypertarget{shild}
    {Шилдт Г. Полный справочник по Java\texttrademark Java SE\texttrademark
        6 Edition. --- 2007.}
\end{thebibliography}



\end{document}
